---
title: "DSA Marketing Campaign"
author: "Thomas Steiner"
date: "2/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Possible Improvements to the Bank's Marketing Campaign

Thanks for letting our team review your marketing campaign prediction model. The opportunity is appreciated. 

The goal of this meeting is to show you the value of your data.

```{r libs}
library(tidyverse)
```

## Performance of the current model at predicting subscribers

We measured the performance of your current predictive model. It is able to predict at 

```{r pressure}
campaign <- read_csv("DSA Data Set.csv")

# Data set includes predictor variable "ModelPrediction"
# Determine the subscription probability with the most accurately predicted results


 # Add a binary variable to data set using the percentage found above
 # ModelPredictionBinary : Yes/No prediction of subscription status
campaign <- mutate(campaign, ModelPredictionBinary = if_else(ModelPrediction >.5, "No", "Yes"))
```

